%!TEX root = ../assignment1.tex

\section{Conclusion}

In this article, we have discussed what makes IT deployment successful by the following procedure of introduction, methodology, findings of Phase 1, findings of Phase 2, outcome, conclusion, summary and reflections. 


In introduction, a brief information has been given, stating what we are investigating and what result we will produce. 3 keywords of project management, change management and risk management have been introduced to fund our further research. The methodology have covered how we do our qualitative analysis, how the evaluation is designed and how to make our own evaluation tool. A subsequent findings of Phase 1 has presented with the primary themes we identified with some samples of our findings in each theme. They are control, people, process and structure. We have also done the evaluation process for the proposals to select the solutions in this phase. As a result, 21 solutions have been selected. The findings of Phase 2 is structurally similar to the previous section, but with 10 case studies. The same primary themes have been identified as well. We have provided some samples in each primary themes as well. With the same evaluation process, we have selected 21 solutions in evaluation process. In outcome, we have analyzed the findings of both phases and found that there is a certain degree of agreement in the findings of the two phases. We have proceed to create our own evaluation tool with the predefined method in the methodology, which has produced a mark sheet for practitioners to use. In conclusion, we look back what we have done section by section.
